---
title: "Netherlands Coronavirus Statistics"
bibliography: mybib.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Now I use some essential table functions in R to do a brief analysis about Netherlands Coronavirus data.It helps people to have a better data visualisation.

The data of generating table below comes from coronavirus repository of RamiKrispin,who provides a tidy format dataset of the 2019 Novel Coronavirus COVID-19 (2019-nCoV) epidemic.The raw data pulled from the Johns Hopkins University Center for Systems Science and Engineering (JHU CCSE) Coronavirus repository.
https://github.com/RamiKrispin/coronavirus
https://github.com/CSSEGISandData/COVID-19

```{r load-packages,echo=FALSE,message=FALSE}
library("tidyverse")
library("DT")
library("plotly")
library("readr")
library("kableExtra")
library("janitor")
library("tibble")
```

```{r data_citation,echo=FALSE,message=FALSE,warning=FALSE}
coronavirus <- read_csv("coronavirus.csv")
coronavirus_Netherlands <- coronavirus%>%
  filter(country=="Netherlands")
```

<br>
The table below shows the total number of infected, deaths and recovered in Netherlands from 2020.01.22 to 2020.08.29.

```{r table1,echo=FALSE,message=FALSE,warning=FALSE}
total_confirmed <- coronavirus_Netherlands%>%
  filter(type == "confirmed")%>%
  summarise(total_confirmed=sum(cases))
total_death <- coronavirus_Netherlands%>%
  filter(type == "death")%>%
  summarise(total_death=sum(cases))
total_recovered <- coronavirus_Netherlands%>%
  filter(type == "recovered")%>%
  summarise(total_recovered=sum(cases))
total_case <- tibble(total_confirmed,total_death,total_recovered)%>%
  kable(align="c",caption="Number of infected, deaths and recovered in Netherlands(by the end of 2020.08.29)") %>% 
  kable_styling()
total_case
```

The plot below
```{r table2,echo=FALSE,message=FALSE,warning=FALSE}
coronavirus_Netherlands_summary <- coronavirus_Netherlands%>%
  group_by(date,type)%>%
  summarise(total=sum(cases))%>%
  pivot_wider(names_from=type,values_from=total)
coronavirus_Netherlands_summary%>%
   DT::datatable(caption="Number of confirmed, deaths and recovered in Netherlands")
```




```{r table3,echo=FALSE,message=FALSE,warning=FALSE}
death_age <- tribble(~"<50",~"50-59",~"60-69",~"70-79",~"80-89",~">90",
                           "46","147","506","1655","2686","1167")
sumdeath0825 <- sum(46,147,506,1655,2686,1167)
death_age <- death_age%>%
  mutate(Total=as.character(sumdeath0825))%>%
  pivot_longer(everything(),names_to="age/gender")%>%
  mutate(pro=as.numeric(value)/sumdeath0825)%>%
  mutate(male=pro*0.5498,
         female=pro*0.4502)%>%
  mutate(Total=male+female)
death_age%>%
  select("age/gender",male,female,Total)%>%
  adorn_pct_formatting(digits=2)%>%
  kable()%>%
  kable_styling()
  


```

deaths(%male):54.98% deaths(%female):45.02%

*  *  *  *
